---
title: "Geog 533 Midterm Exam"
author: "Your name"
output: 
  html_notebook:
    toc: TRUE
    toc_float: TRUE
---

## What to submit:
An **R notebook/html document** that contains the script/output for each question.Use the provided **Geog533_midterm_template.Rmd** to complete your answers and generate the html document. File name convention for submissions: lastname_firstname_midterm.zip. You have 60 minutes (8:30-9:30 am) to complete the exam. There will be a 10% penalty per 10 minutes for late submissions.  

## Question 1 (20 pt.)
The **iris** data set in the **datasets** package contains 150 cases (rows) and 5 variables (columns). 

### Question 1a
Randomly select half of the cases as training dataset and the remaining half as test dataset. 
```{r, message=FALSE, warning=FALSE}

```

### Question 1b
Find out the number of each species (*setosa, versicolor, and virginica*) in the training and test datasets, respectively. 
```{r}

```

## Question 2 (20 pt.)
Assume that the probabilities of boy and girl births are **0.505** and **0.495**, respectively. 

### Question 2a
What’s the probability of having exactly 50 boys out of 100 births? **(X = 50)**
```{r}

```


### Question 2b
What’s the probability of having more than 60 boys out of 100 births? **(X > 60)**
```{r}

```



### Question 2c
What’s the probability of having between 40 and 60 boys out of 100 births? **(40 < X ≤ 60)**
```{r}

```


### Question 2d
Plot the density function of the number of boy births out of 100. 
```{r}

```



## Question 3 (20 pt.)
If cars arrive randomly at a traffic light following posission distribution at the rate of five every ten seconds. 

### Question 3a
What the probability that exactly 30 cars arrive in the next minute (60 seconds)? (X=30)
```{r}

```


### Question 3b
What’s the probability that more than 40 cars arrive in the next minute (60 seconds)? (X>40)
```{r}

```


### Question 3c
What’s the probability that between 20 and 40 cars arrive in the next minute (60 seconds)? (20<X≤40)
```{r}

```


### Question 3d
Plot the density function of 0-100 cars arriving in the next minute (60 seconds).
```{r}

```



## Question 4 (20 pt.)
The number of customers at a bank each day is found to be normally distributed with mean µ = 250 and standard deviation σ=80. 

### Question 4a
What fraction of days will have more than 300 customers? (X>300)
```{r}

```


### Question 4b
What number of customers will be exceeded 10% of the time?
```{r}

```


### Question 4c
What fraction of days will have between 200 and 300 customers? (200 < X≤ 300)
```{r}

```


### Question 4d
Plot the density function and create the shaded area between 200 and 300 customers.
```{r}

```


## Question 5 (20 pt.)
The average time between floods in Binghamton is found to be 4.3 year. Assuming that the distribution of times between floods is exponential. (20 pt.)

### Question 5a
What is the likelihood that the time until the next flood will be shorter than one year?
```{r}

```


### Question 5b
What is the likelihood that the time until the next flood will be longer than three years? 
```{r}

```


### Question 5c
What is the likelihood that the time until the next flood is between four and seven years?
```{r}

```


### Question 5d
What is the likelihood that time until the next flood is greater than seven years, given that it is greater than four years? 
```{r}

```
